Bayesian phylogenetic estimation of fossil ages

### 2015-09-02 fossilDating.tex
updated figures

\textcite{gavryushkina2015bayesian} described a ``total-evidence'' approach to the phylogenetic estimation of time-trees that employed both fossil and molecular sequence data as equal partners under the rule of probability. We extend their work further by investigating the consistency between the estimated phylogenetic age of a fossil and the corresponding palaeontological age range based on radiometrically-dated geological strata. The model of time-tree phylogeny employed is the so-called fossilized birth-death process \autocite{Heath2014}, which forms a prior probability distribution on the space of sampled-ancestor trees \autocite{Gavr2013}.

@@

First we determined $p(t|M_\mathcal{T})$ for the prior distributions as in \cite{Gavryushkina2014} ($T: Unif(0,160), d: lognorm(-3.5,1.5), r: Unif(0,1), s: Unif(0,1)$). This prior specification leads to a distribution of sampling time with almost all mass close to the present (xxx give precise values, Figure xxx, black line). 
Second we  determined $p(t|M_\mathcal{T})$ for the prior distributions ($T: Unif(0,160), d: lognorm(-3.5,0.5), r: Unif(0,1), s: Unif(0,1)$). This produces a prior where larger sampling times have a non-negligable weight (Figure xxx, red line).

>>>>

\textcite{gavryushkina2015bayesian} described a ``total-evidence'' approach \autocite[implemented in BEAST2;][]{Beast2} for phylogenetic estimation of time-trees that employs both fossil and molecular sequence data as equal partners under the rule of probability. We extend their work further by investigating the consistency between the estimated phylogenetic age of a fossil and the corresponding palaeontological age range based on radiometrically-dated geological strata. The model of time-tree phylogeny employed is the so-called fossilized birth-death process \autocite{Heath2014}, which forms a prior probability distribution on the space of sampled-ancestor trees \autocite{Gavr2013}.

@@

First we determined $p(t|M_\mathcal{T})$ for the prior distributions as in \autocite{gavr2014} ($T: Unif(0,160), d: lognorm(-3.5,1.5), r: Unif(0,1), s: Unif(0,1)$). This prior specification leads to a distribution of sampling time with almost all mass close to the present (xxx give precise values, Figure xxx, black line). 
Second we  determined $p(t|M_\mathcal{T})$ for the prior distributions ($T: Unif(0,160), d: lognorm(-3.5,0.5), r: Unif(0,1), s: Unif(0,1)$). This produces a prior where larger sampling times have a non-negligable weight (Figure xxx, red line).
